Polytope notes

### 2020-01-23 notes/polytope-notes.tex
added restatement of optimality conditions to note

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\epi}{\text{epi}}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

@@

  \section{Necessary and sufficient conditions for optimality}
  \subsection{Necessary conditions}
    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.

>>>>

\newcommand{\Opt}{\mathrm{Opt}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\epi}{\text{epi}}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

@@

  \section{Necessary and sufficient conditions for optimality}
  In this section, we have a collection of polytopes $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.
  Given a vector $p \in \reals^n$ (for us, always a probability distribution), we write the $p$-weighted Minkowski sum of $\T^r$ as
    \[ \oplus_p \T^r := \oplus_{y \in \Y} p(y) T^r_y , \]
  where $p(y) T^r_y = \{ p(y) x : x \in T^r_y\}$, i.e. the set $T^r_y$ scaled by $p(y)$, and the Minkowski sum of these $|\Y|$ scaled sets consists of all points $x$ that can be written as a sum of points, one from each set.

  Recall the optimality condition:
  \begin{definition}[Optimality of subgradients for a level set]
    Given a collection of polytopes $\T = \{T_y \subseteq \reals^d : y \in \Y\}$ and a polytope $C \subseteq \Delta_{\Y}$, the \emph{optimality condition $\Opt(\T, C)$ holds} if $p \in C$ if and only if $\vec{0} \in \oplus_p T_y$.
  \end{definition}

  Recall the main characterization theorem:
  \begin{theorem}
    Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} p \cdot \ell(r)\}$.
    Then $\ell$ is $d$-embeddable if and only if there exist polytopes $\{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$ such that both of the following hold:
    \begin{enumerate}
      \item (Optimality) For all $r \in \R$, we have $\Opt(\T^r, \gamma_r)$.
      \item (Monotonicity) (TODO)
    \end{enumerate}
  \end{theorem}

  \subsection{Necessary conditions}
    With the above results, we actually realize that the matrix $B$ captures a necessary condition for optimality.
    As we showed earlier, we derive the support matrix $E$ such that $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$ by substitution, and in Proposition~\ref{prop:relate-rows}, derive necessary and sufficient conditions on the matrix $B$ such that the optimality condition ($\vec 0$ in the weighted Minkowski sum) holds, and these conditions are in relation to the support matrix $E$.
